Reproducible Research: Peer Assessment 1
========================================


## Loading and preprocessing the data
```{r echo = T}
unzip("activity.zip")
activityData <- read.csv("activity.csv")
```

## What is the mean total number of steps taken per day?

### Histogram of the total number of steps taken each day

```{r echo = T}
stepsPerDate <- aggregate(steps ~ date, data = activityData, FUN = sum)
barplot(stepsPerDate$steps, names.arg=stepsPerDate$date, xlab="date", ylab="steps")
```

### **mean** and **median** total number of steps taken per day

```{r echo = T}
mean(stepsPerDate$steps)
median(stepsPerDate$steps)
```


## What is the average daily activity pattern?

### Make a time series plot (i.e. `type = "l"`) of the 5-minute
   interval (x-axis) and the average number of steps taken, averaged
   across all days (y-axis)

```{r echo = T}
stepsPerInterval <- aggregate(steps ~ interval, data = activityData, FUN = mean)
plot(stepsPerInterval, type = "l")
```

### Which 5-minute interval, on average across all the days in the
   dataset, contains the maximum number of steps?

```{r echo = T}
stepsPerInterval$interval[which.max(stepsPerInterval$steps)]
```

